Chapter 16: Particle-laden gravity currents: the lock-release slumping regime at the laboratory scale

### 2024-03-14 paper/reply_to_referees/reply.tex
small modifs
Last modifs

@@

    \item \MinorReply{Line 211-212}{what does it mean 2D vertical and turbulence averaged? Are these 2D RANS simulations? Are the 2 coordinates horizontal, since vertical is averaged?}{\julien{julien}}

@@

    \item \MinorReply{figure 2}{some of the volume fraction data goes to 1.}{\marie{marie}}

>>>>

%__________________________________________________________________________
\newpage
\section{Reply to referee 2}

@@

    \item \MinorReply{Line 211-212}{what does it mean 2D vertical and turbulence averaged? Are these 2D RANS simulations? Are the 2 coordinates horizontal, since vertical is averaged?}{Indeed, 2D vertical and turbulence-averaged means 2D RANS. Only turbulence is averaged the wall-normal direction is not. The sentence has been modified to clarify this.}

@@

    \item \MinorReply{figure 2}{some of the volume fraction data goes to 1.}{Indeed, hydrogel particles are deformable. As a consequence, at rest, they experience deformation under the weight of the particles above, hence resulting in denser packing compared to hard spheres, close to 1 for the smallest hydrogel particles used here. This was already mentioned in the description of Dataset 2, so we did not modify the text.}
